---
title: "Segmentation"
author: "Leyla Agahayrli"
date: "10"
output: html_document
---

```{r setup, include=FALSE}

library("readr")

install.packages("cluster")
install.packages("factoextra")
install.packages("metricsgraphics")
install.packages("scales")
install.packages("ggplot2")
install.packages("dplyr")
install.packages("rlang")
install.packages('tidyverse')
library(dplyr)
library(ggplot2)
library(rlang)
library(DT)
library(lubridate)
library(scales)
library(plotly)
library(cluster)
library(factoextra)
library(metricsgraphics)
library(tidyverse)
install.packages("purrr")
library(purrr)

```



```{r cars}
data <- read.table(file ="C:/Users/user/Documents/R/transaction", header = TRUE, sep=";")
head(data)
colnames(data)[colnames(data)%in% c("X8345", "X4342", "SE")]<- c("ID", "Amount", "Country")
summary(data)
str(data)
data=na.omit(data)

```
#density plot  outlier are the transaction amount higher than 50000$

```{r, echo=FALSE}
library(scales)
ggplot(data) + geom_density(aes(x=Amount)) +
  scale_x_continuous(labels=dollar)

```
#boxplot  

```{r, echo=FALSE}



a=table(data$Debit)
barplot(a,main="Using BarPlot to display trabsaction type",
        ylab="Count",
        xlab="trabsaction type",
        col=rainbow(2),
        legend=rownames(a))

ggplot(data) +
  geom_bar(aes(x=Country, fill=Debit), position="dodge")

```

#credit transaction higher than debit (amount)
```{r, echo=FALSE}

p<-ggplot(data, aes(x=Debit, y=Amount)) +geom_violin(trim=FALSE)
p


```
#####Convert category(country) to numeric### 1=FI//2=DK//3=SE//4=RO

```{r, echo=FALSE}

ranks<-rank(-table(data$Country), ties.method="first")
data<-data.frame(data, COUNTRY=ranks[as.character(data$Country)])
#Amount and Country for clustring
data1<-data[,c(3,5)]



```

###k mean cluster

```{r, echo=FALSE}

install.packages("purrr")
library(purrr)
set.seed(123)
# function to calculate total intra-cluster sum of square 
iss <- function(k) {
  kmeans(data1,k,iter.max=100,nstart=100,algorithm="Lloyd" )$tot.withinss
}
k.values <- 1:10
iss_values <- map_dbl(k.values, iss)
plot(k.values, iss_values,
     type="b", pch = 19, frame = FALSE, 
     xlab="Number of clusters K",
     ylab="Total intra-clusters sum of squares")


```
###aS A RESULT OF ELBOW METHOD, 4 CLUSTER HAVE BEEN CHOOSEN


```{r, echo=FALSE}
set.seed(123)
km.res <- kmeans(scale(data1), 4, nstart = 25)
print(km.res)
km.res$size
km.res$cluster
km.res$centers

```
##Plotting cluster for 2 dimention Amount and Location
##from AML perspective potential risk attributes are transaction type, geography, transaction amount.
#As the possibility of high repititive number of small transaction and money flows in, out of high risk countries attentiom should be paid, I adressed to this two dimention segment

```{r, echo=FALSE}
fviz_cluster(km.res, data = data1,
             palette = c("#2E9FDF","#00AFBB", "#E7B800", "#FC4E07"),
             ellipse.type = "convex",
             star.plot = TRUE, # Add segments from centroids to items
             repel = TRUE, # Avoid label overplotting (slow)
             ggtheme = theme_minimal()
)

```

###Step2####

###k-means clustring for outlier detection

```{r, echo=FALSE}
centers<-km.res$centers[km.res$cluster,]
centers
distances<-sqrt(rowSums((data1-centers)^2))
distances
#Identify a minimum of 5 customer IDs connected to transactions that do not fit into the customer's own typical behavior

outliers<-order(distances, decreasing=T)[1:5]

print(outliers)  
print(data[outliers,]) #as  behavioring these 5 ID are outlier and show exceptional transactional performance



```
#plotting outliers

```{r, echo=FALSE}

plot(data1[,c("COUNTRY", "Amount")], pch=19, col=km.res$cluster, cex=1)

points(km.res$centers[,c("COUNTRY", "Amount")], col=1:3, pch=15, cex=2)

points(data1[outliers, c("COUNTRY", "Amount")], pch="+", col=4, cex=3)



```
